### 2023-08-10 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny2

\section{Conclusions \label{sec:conclusion}}
In this work we used numerical simulations to examine the hydrodynamics of a multicomponent vesicle under strong confinement, which is a ubiquitous configuration in biology when a cell squeezes through a small channel. We refined the phase-field formulation in \citet{liu-mar-li-vee-low2017} with a new bending model that uses a sigmoidal function for the bending stiffness to retain positiveness in the bending modulus. The linear model \cite{liu-mar-li-vee-low2017} works well for a vesicle in free-space. However, under strong confinement we find it necessary to enforce the condition that the dimensionless bending modulus $b(u)$ be in the range of $[\beta,1]$  ($\beta = b_{\min}/b_{\max}$)  to avoid instability in membrane shapes (see \S~\ref{subsec:const_eq}). We focused on the hydrodynamics of a multicomponent vesicle in two types of confinement: a stenosis channel (\S~\ref{subsec:Stenosis}), and a contracting channel (\S~\ref{subsec:Contraction}). For both cases we varied the reduced area $\alpha$, the floppy-to-stiffness ratio $\beta$, the initial distribution of lipid domains with a fixed Capillary number $Ca=0.25$ and a fixed Peclet number of the lipid dynamics $Pe=1$.

>>>>

\section{Conclusions \label{sec:conclusion}}
In this work we used numerical simulations to examine the hydrodynamics of a multicomponent vesicle under strong confinement, which is a ubiquitous configuration in biology when a cell squeezes through a small channel. We refined the phase-field formulation in \citet{liu-mar-li-vee-low2017} with a new bending model that uses a sigmoidal function for the bending stiffness to retain positiveness in the bending modulus. The linear model \cite{liu-mar-li-vee-low2017} works well for a vesicle in free-space. However, under strong confinement we find it necessary to enforce the condition that the dimensionless bending modulus $b(u)$ be in the range of $[\beta,1]$  ($\beta = b_{\min}/b_{\max}$)  to avoid instability in membrane shapes (see \S~\ref{subsec:const_eq}). We focused on the hydrodynamics of a multicomponent vesicle in two types of confinement: a stenosis channel (\S~\ref{subsec:Stenosis}), and a contracting channel (\S~\ref{subsec:Contraction}). For both confining geometries we varied the reduced area $\alpha$, the floppy-to-stiffness ratio $\beta$, and the initial distribution of lipid domains with a fixed Capillary number $Ca=0.25$ and a fixed Peclet number of the lipid dynamics $Pe=1$.  The reason for focusing on
